Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-08-19 Scripts/Initial_Analysis.Rmd
Included value participation on figure 3

    Final_Result <- mean_sd_index %>%
      group_by(taxon_key,neighbour_id,n_ens) %>%
      summarise(emerging_yr= min(year)) %>%
      left_join(EEZ_ids,
                by = "neighbour_id") %>%
      ungroup() %>%
      select(taxon_key,eez_name,eez_neighbour,n_ens,emerging_yr) %>% 
      mutate(Tresh= NA)

@@

    Final_Result <- mean_sd_index %>%
      filter(year > Hist_y) %>%
      mutate(
        Tresh_one = ifelse(trend > (historic_sd$hist_mean+historic_sd$noise) | trend < (historic_sd$hist_mean-historic_sd$noise),"One",NA),
        Tresh_two = ifelse(trend > (historic_sd$hist_mean+(2*historic_sd$noise)) | trend < (historic_sd$hist_mean-(2*historic_sd$noise)),"Two",NA)
      ) %>%
      gather("Tresh","YesNo",Tresh_one,Tresh_two) %>% 
      filter(!is.na(YesNo)) %>% 
      group_by(taxon_key,neighbour_id,n_ens,Tresh) %>%
      summarise(emerging_yr= min(year)) %>%
      left_join(EEZ_ids,
                by = "neighbour_id") %>%
      ungroup() %>%
      select(taxon_key,eez_name,eez_neighbour,n_ens,emerging_yr,Tresh)

@@

@@

World_map <- rnaturalearth::ne_countries(scale = 'small', returnclass = c("sf")) %>%
  # st_transform(crs = "+proj=eck4") %>%
  st_transform(crs = 4326) %>% # 4326
  left_join(World_map_dat,
            by = "iso_a3")

@@

##### Fig. Netowrk

@@

# time <- "per_mid_plot"
time <- "per_early_plot"

@@

Prop_map <- ggplot() +
  geom_sf(data = subset(World_map, sovereignt != "Antarctica"), size = 0.1, fill = "gray50", col = "gray50") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_point(data = subset(Data, time_step == time & per_chng < 0),
             aes(start_lon,
                 start_lat,
                 col = per_chng),
             size = 0.05,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(paths, time_step == time & per_chng > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_chng
            ),
            size = 0.3,
            arrow = arrow(length = unit(0.009, "npc"),
                          ends = "first"),
            show.legend = NA) +
  my_ggtheme_m() +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Data$per_chng)),
    breaks = seq(0,max(Data$per_chng),5),
    # option="magma",
    # direction = -1
  ) +
  ggsave("./Figures/figure_connections_early_n50.png",
  width = 10,
  height = 6,
  units = "in"
  )

@@

gc()
plot_all <- ggdraw() +
      # map
      draw_plot(Prop_map, x = 0, y = 0.45, width = 1, height = 0.58) +
      # Lat America reg plor
      draw_plot(Lat_am_map, x = 0.1, y = 0.08, width = 0.3, height = 0.4) +
      # Europe reg plot
      draw_plot(Eu_map, x = 0.35, y = 0.08, width = 0.3, height = 0.4) +
      # Med regional plot
      draw_plot(Med_map, x = 0.65, y = 0.08, width = 0.3, height = 0.4) +
      draw_plot_label(label = c("a", "b"), 
                      size = 20,
                      x = c(0, 0), 
                      y = c(1, 0.45)
      ) #+
      # draw_plot_label(label = c("Revenue (USD) | Catch (Tonnes)","(Million)"), 
                      # size = 8,
                      # x = c(0.325,0.485), 
                      # y = c(0.31,0.29)
      )

    save_plot(
      # paste(Figures_Path,"100_25_Bins_Value_Region.png",sep=""),
      "test.png",
      plot_all,
      base_height = 8,
      base_width = 8
    )

@@

##### Histogram of change

@@

 results %>% 
  gather("time_step","change",per_early,per_mid) %>% 
  filter(variable == "mean_eez" & 
           !is.na(change)
         ) %>%
ggplot() +
  geom_density(
               aes(
                 x = ifelse(change >= 100,100,change),
                 # x = change,
                 fill = ifelse(time_step == "per_early","q",time_step)
                 # fill = time_step,

@@

####  Year of Eergence Analysisç

@@

# First time a Species becomes emergent
Eme_Res %>% 
  filter(
    n_ens == 10#,
    # Tresh == "Tresh_one"
  ) %>% 
  group_by(Tresh,taxon_key,emerging_yr) %>% 
  summarise(
    n_trans = length(unique(eez_name))
  ) %>% 
  group_by(Tresh,taxon_key) %>% 
  summarise(
    ntrans = min(emerging_yr)
  ) %>% 
  group_by(Tresh,ntrans) %>% 
  summarise(
    n_taxa = length(unique(taxon_key))
  ) %>% 
  arrange(-n_taxa) %>% 
  # View()
  # group_by(Tresh) %>% 
  # summarise(sum(n_taxa))
  ggplot() +
  geom_line(
    aes(
      x = ntrans,
      y = n_taxa,
      color = Tresh
    )
  )

# EEZ, first time an EEZ has a emergent stock
Eme_Res %>% 
  filter(
    n_ens == 10#,
    # Tresh == "Tresh_one"
  ) %>% 
  group_by(Tresh,eez_name,emerging_yr) %>% 
  summarise(
    n_trans = length(unique(taxon_key))
  ) %>% 
  group_by(Tresh,eez_name) %>% 
  summarise(
    ntrans = min(emerging_yr)
  ) %>% 
  group_by(Tresh,ntrans) %>% 
  summarise(
    n_taxa = length(unique(eez_name))
  ) %>% 
  arrange(-n_taxa) %>% 
  View()
  # group_by(Tresh) %>%
  # summarise(sum(n_taxa))
  # ggplot() +
  # geom_line(
  #   aes(
  #     x = ntrans,
  #     y = n_taxa,
  #     color = Tresh
  #   )
  # )

# Numer of EEZs where stocks will emerge
stock_d_hist <- Eme_Res %>% 
  distinct(taxon_key,neighbour_id,Tresh, .keep_all = TRUE) %>%
  group_by(emerging_yr,taxon_key,Tresh) %>%
  summarise(n_tax = length(unique(eez_name))) %>%
  # summarise(n()) %>% 
  mutate(
    level = "EEZs per Spp"
  )  %>% 
  ungroup() %>% 
  select(-taxon_key)

# Per EEZs
eez_d_hist <- Eme_Res %>% 
  distinct(taxon_key,neighbour_id,Tresh, .keep_all = TRUE) %>%
  group_by(emerging_yr,eez_name,Tresh,neighbour_id) %>%  
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(n()) %>% 
  mutate(
    level = "Spp per EEZ"
  ) %>% 
  ungroup() %>% 
  select(-eez_name)

stock_d_hist %>% 
  bind_rows(eez_d_hist) %>% 
  filter(Tresh != "NA") %>% 
  ggplot() +
  geom_density(
    aes(
      x = emerging_yr,
      fill = level
    ),
    stat = "count",
    alpha= 0.8,
    size=0.5,
  ) +
  scale_y_continuous("Frequency",
                     # breaks = seq(0,300,50),
                     # limits = c(0,300)
  ) +
  scale_x_continuous("Year of emergence",
                     # breaks = seq(2006,2100,25),
                     # limits = c(2000,2100)
  ) +
  my_ggtheme_p() +
  scale_fill_viridis(discrete = T) +
  facet_wrap(~Tresh) +
  ggsave("./Figures/hist_freq.png",
         width = 6,
         height = 6,
         units = "in"
  )

@@

# Per Stock
stock_d <-  Eme_Res %>% 
  left_join(Neighbours) %>% 
    # distinct(taxon_key,neighbour_id, .keep_all = TRUE) %>% 
    group_by(taxon_key,Tresh) %>% 
    summarise(
      taxon_emer = min(emerging_yr)
    ) %>% 
    group_by(taxon_emer,Tresh) %>% 
  summarise(
    n_tax = n()
  ) %>% 
  group_by(Tresh) %>% 
  mutate(
    com_sum = cumsum(n_tax),
    level = "Stock"
  )

  #  EEZ data
eez_d <-  Eme_Res %>% 
  left_join(Neighbours) %>% 
  filter(n_ens == 10) %>% 
    # distinct(eez_name,neighbour_id, .keep_all = TRUE) %>% 
    group_by(eez_name,Tresh) %>% 
    summarise(
      taxon_emer = min(emerging_yr)
    ) %>% 
    group_by(taxon_emer,Tresh) %>% 
  summarise(
    n_tax = n()
  ) %>% 
  group_by(Tresh) %>% 
  mutate(
    com_sum = cumsum(n_tax),
    level = "EEZ"
  )

# Plot Data
plot_data <- stock_d %>% 
  bind_rows(eez_d) %>% 
  filter(Tresh != "NA") %>% 
  mutate(
    total = ifelse(level == "Stock",length(unique(Eme_Res$taxon_key)),length(unique(Eme_Res$eez_name))),
    per = com_sum/total*100
  ) ;plot_data

  # filter(emerging_yr >= 2020) %>% 
  ggplot() +
    geom_area(data = subset(plot_data, level == "Stock"),
              aes(
                x = as.numeric(taxon_emer),
                y = com_sum,
                fill = level
              ),
              alpha= 0.8,
              size=0.5,
              colour="black"
    )  +
    geom_area(data = subset(plot_data, level == "EEZ"),
              aes(
                x = taxon_emer,
                y = com_sum,
                fill = level
              ),
              alpha= 0.8,
              size=0.5,
              colour="black"
    ) +
    facet_wrap(~Tresh) + 
    # Comment out for option A (Change plot name!!)
  #   geom_hline(yintercept = length(unique(Eme_Res$eez_name)), color = "grey",linetype = "dashed") +
  # geom_text(aes(label="Total number of EEZs", x = 2010, y = length(unique(Eme_Res$eez_name))+10), color = "grey70",size =3) +
  #   geom_hline(yintercept = length(unique(Eme_Res$taxon_key)), color = "grey",linetype = "dashed") +
  # geom_text(aes(label="Total number of Taxa", x = 2010, y = length(unique(Eme_Res$taxon_key))+10), color = "grey70",size =3) +
    scale_y_continuous("Cumulatuve Curve",
                       breaks = seq(0,600,50),
                       limits = c(0,600)
    ) +
    scale_x_continuous("Year of emergence",
                       breaks = seq(2005,2100,10),
                       limits = c(2005,2100)
    ) +
    my_ggtheme_p() +
    scale_fill_viridis(discrete = T) +
  ggsave("./Figures/figure_accumulative_curve_ab.png",
         width = 6,
         height = 6,
         units = "in"
  )

@@

  # filter(emerging_yr >= 2020) %>% 
  ggplot() +
    geom_area(data = subset(plot_data, level == "Stock"),
              aes(
                x = as.numeric(taxon_emer),
                y = per,
                fill = level
              ),
              alpha= 0.8,
              size=0.5,
              colour="black"
    )  +
    geom_area(data = subset(plot_data, level == "EEZ"),
              aes(
                x = taxon_emer,
                y = per,
                fill = level
              ),
              alpha= 0.8,
              size=0.5,
              colour="black"
    ) +
    scale_y_continuous("Cumulatuve Curve",
                       breaks = seq(0,100,25),
                       limits = c(0,100)
    ) +
    scale_x_continuous("Year of emergence",
                       breaks = seq(2005,2100,10),
                       limits = c(2005,2100)
    ) +
    my_ggtheme_p() +
    scale_fill_viridis(discrete = T) +
    facet_wrap(~Tresh) + 
  ggsave("./Figures/figure_accumulative_curve_per.png",
         width = 6,
         height = 6,
         units = "in"
  )

@@

##### Mapping the time of emergence

@@

# Per EEZs
eez_d_hist <- Eme_Res %>% 
  group_by(eezid  = sf_eezid,fishing_entity,tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(
    mean_yr = mean(emerging_yr,na.rm=T),
    sd_yr = sd(emerging_yr,na.rm=T),
    n_taxa = length(unique(taxon_key))
    ) %>% 
  gather("metric","value",mean_yr:n_taxa)

@@

fish_d_hist <- Eme_Res %>% 
  group_by(fishing_entity,tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(
    value = length(unique(taxon_key))
    ) %>% 
  filter(!is.na(fishing_entity))

@@

ggplot(eez_d_hist) +
  geom_density(
    aes(
      x = value,
      fill = Tresh
    ),
    bins = 10,
    alpha = 0.8
  ) +
  facet_wrap(~metric,
             scales = "free") +
  scale_fill_viridis(discrete = T) +
  my_ggtheme_p() +
  ggsave("./Figures/hist_mean.png",
         width = 6,
         height = 6,
         units = "in"
  )

World_map_nemer <- World_map %>%
  mutate(fishing_entity = ifelse(fishing_entity == "United States","USA", fishing_entity)) %>% 
  left_join(fish_d_hist,
            by = "fishing_entity")

@@

  Tresh_list <- c("Tresh_one","Tresh_two")
  name_save <- paste("./Figures/emer_map_",Tresh_list[i],".png")

  map <- World_eez_sf %>% 
    left_join(eez_d_hist,
              by = "eezid") %>% 
    filter(tresh == Tresh_list[i],
           metric == "mean_yr") %>% 
    ggplot() +
    geom_sf(
      aes(
        fill = value
      ),
      color =  "white",
      size = 0.1
    ) +
    geom_sf(data = World_map_nemer, aes(fill = value +2000   # to match scales
                                        ),
      color =  "white",
      size = 0.1
      ) +
    annotate("text", 
             x =(c(-85.5,-30,25,81,136)+5),
             y = -93.5,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100), 
             color="black", 
             size=3, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    scale_fill_viridis(
      limits = c(2000,2100),
      breaks = seq(2000,2100,25)
    ) +
    my_ggtheme_m() +
    ggsave(name_save,
           width = 12,
           height = 10,
           units = "in"
    )

>>>>

    Final_Result <- mean_sd_index %>%
      group_by(taxon_key,neighbour_id,n_ens) %>%
      summarise(emerging_yr= min(year)) %>%
      left_join(EEZ_ids,
                by = "neighbour_id") %>%
      ungroup() %>%
      select(taxon_key,eez_name,eez_neighbour,n_ens,emerging_yr) %>% 
      mutate(tresh= NA)

@@

    Final_Result <- mean_sd_index %>%
      filter(year > Hist_y) %>%
      mutate(
        tresh_one = ifelse(trend > (historic_sd$hist_mean+historic_sd$noise) | trend < (historic_sd$hist_mean-historic_sd$noise),"One",NA),
        tresh_two = ifelse(trend > (historic_sd$hist_mean+(2*historic_sd$noise)) | trend < (historic_sd$hist_mean-(2*historic_sd$noise)),"Two",NA)
      ) %>%
      gather("tresh","YesNo",tresh_one,tresh_two) %>% 
      filter(!is.na(YesNo)) %>% 
      group_by(taxon_key,neighbour_id,n_ens,tresh) %>%
      summarise(emerging_yr= min(year)) %>%
      left_join(EEZ_ids,
                by = "neighbour_id") %>%
      ungroup() %>%
      select(taxon_key,eez_name,eez_neighbour,n_ens,emerging_yr,tresh)

@@

# --------------- #
# Load SAU catch and revenue data
# --------------- #

Sau_data <-fread(paste(my_path("D"),"SAU/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>%
  clean_names() %>% 
  # Remove high seas and 207 and 208 that are unknown
  filter(!fishing_entity_id %in% c(213,223)) %>%  # 207,208
  # Allocate catch of islands to UK
  mutate(fishing_entity_id = ifelse(fishing_entity_id %in% c(219,220), 183,fishing_entity_id)) %>% 
  # Convert to 2019 real USD
  mutate(values = 1.16 * value) %>%
  # Average 10 years of data
  group_by(fishing_entity_id,taxon_key) %>% 
  summarise_at(c("catch","value"),
               mean,na.rm=T) %>% 
  gather("variable","value",catch:value)

@@

World_map <- rnaturalearth::ne_countries(scale = 'small', returnclass = c("sf")) %>%
  clean_names() %>% 
  # st_transform(crs = "+proj=eck4") %>%
  st_transform(crs = 4326) %>% # 4326
  left_join(World_map_dat,
            by = "iso_a3")

@@

##### Fig. 2 and S1. (Netowrk)

@@

time <- "per_mid_plot"
# time <- "per_early_plot"

@@

Prop_map <- ggplot() +
  geom_sf(data = subset(World_map, sovereignt != "Antarctica"), size = 0.1, fill = "gray50", col = "gray50") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_point(data = subset(Data, time_step == time & per_chng < 0),
             aes(start_lon,
                 start_lat,
                 col = per_chng),
             size = 0.05,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(paths, time_step == time & per_chng > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_chng
            ),
            size = 0.3,
            arrow = arrow(length = unit(0.009, "npc"),
                          ends = "first"),
            show.legend = NA) +
  my_ggtheme_m() +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Data$per_chng)),
    breaks = seq(0,max(Data$per_chng),5),
    # option="magma",
    # direction = -1
  ) +
  ggsave("./Figures/figS1a.png",
  width = 10,
  height = 6,
  units = "in"
  )

@@

# gc()
# plot_all <- ggdraw() +
#       # map
#       draw_plot(Prop_map, x = 0, y = 0.45, width = 1, height = 0.58) +
#       # Lat America reg plor
#       draw_plot(Lat_am_map, x = 0.1, y = 0.08, width = 0.3, height = 0.4) +
#       # Europe reg plot
#       draw_plot(Eu_map, x = 0.35, y = 0.08, width = 0.3, height = 0.4) +
#       # Med regional plot
#       draw_plot(Med_map, x = 0.65, y = 0.08, width = 0.3, height = 0.4) +
#       draw_plot_label(label = c("a", "b"), 
#                       size = 20,
#                       x = c(0, 0), 
#                       y = c(1, 0.45)
#       ) #+
#       # draw_plot_label(label = c("Revenue (USD) | Catch (Tonnes)","(Million)"), 
#                       # size = 8,
#                       # x = c(0.325,0.485), 
#                       # y = c(0.31,0.29)
#       )
#     
#     
#     save_plot(
#       # paste(Figures_Path,"100_25_Bins_Value_Region.png",sep=""),
#       "test.png",
#       plot_all,
#       base_height = 8,
#       base_width = 8
#     )

@@

##### Fig S2 (Histogram of change)

@@

 Prop_results %>% 
  gather("time_step","change",per_early,per_mid) %>% 
  filter(variable == "mean_eez" & 
           !is.na(change)
         ) %>%
ggplot() +
  geom_density(
               aes(
                 x = ifelse(change >= 100,100,change),
                 # x = change,
                 fill = ifelse(time_step == "per_early","q",time_step)
                 # fill = time_step,

@@

####  Year of Eergence Analysis

@@

# First time a Species becomes emergent
Eme_Res %>% 
  filter(
    n_ens == 10#,
    # tresh == "tresh_one"
  ) %>% 
  group_by(tresh,taxon_key,emerging_yr) %>% 
  summarise(
    n_trans = length(unique(sf_eez_name))
  ) %>% 
  group_by(tresh,taxon_key) %>% 
  summarise(
    ntrans = min(emerging_yr)
  ) %>% 
  group_by(tresh,ntrans) %>% 
  summarise(
    n_taxa = length(unique(taxon_key))
  ) %>% 
  arrange(-n_taxa) %>% 
  # View()
  # group_by(tresh) %>% 
  # summarise(sum(n_taxa))
  ggplot() +
  geom_line(
    aes(
      x = ntrans,
      y = n_taxa,
      color = tresh
    )
  )

# EEZ, first time an EEZ has a emergent stock
Eme_Res %>% 
  filter(
    n_ens == 10#,
    # tresh == "tresh_one"
  ) %>% 
  group_by(tresh,sf_eez_name,emerging_yr) %>% 
  summarise(
    n_trans = length(unique(taxon_key))
  ) %>% 
  group_by(tresh,sf_eez_name) %>% 
  summarise(
    ntrans = min(emerging_yr)
  ) %>% 
  group_by(tresh,ntrans) %>% 
  summarise(
    n_taxa = length(unique(sf_eez_name))
  ) %>% 
  arrange(-n_taxa) %>% 
  View()
  # group_by(tresh) %>%
  # summarise(sum(n_taxa))
  # ggplot() +
  # geom_line(
  #   aes(
  #     x = ntrans,
  #     y = n_taxa,
  #     color = tresh
  #   )
  # )

# Numer of EEZs where stocks will emerge
stock_d_hist <- Eme_Res %>% 
  distinct(taxon_key,neighbour_id,tresh, .keep_all = TRUE) %>%
  group_by(emerging_yr,taxon_key,tresh) %>%
  summarise(n_tax = length(unique(sf_eez_name))) %>%
  # summarise(n()) %>% 
  mutate(
    level = "EEZs per Spp"
  )  %>% 
  ungroup() %>% 
  select(-taxon_key)

# Per EEZs
eez_d_hist <- Eme_Res %>% 
  distinct(taxon_key,neighbour_id,tresh, .keep_all = TRUE) %>%
  group_by(emerging_yr,sf_eez_name,tresh,neighbour_id) %>%  
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(n()) %>% 
  mutate(
    level = "Spp per EEZ"
  ) %>% 
  ungroup() %>% 
  select(-sf_eez_name)

stock_d_hist %>% 
  bind_rows(eez_d_hist) %>% 
  filter(tresh != "NA") %>% 
  ggplot() +
  geom_density(
    aes(
      x = emerging_yr,
      fill = level
    ),
    stat = "count",
    alpha= 0.8,
    size=0.5,
  ) +
  scale_y_continuous("Frequency",
                     # breaks = seq(0,300,50),
                     # limits = c(0,300)
  ) +
  scale_x_continuous("Year of emergence",
                     # breaks = seq(2006,2100,25),
                     # limits = c(2000,2100)
  ) +
  my_ggtheme_p() +
  scale_fill_viridis(discrete = T) +
  facet_wrap(~tresh) +
  ggsave("./Figures/hist_freq.png",
         width = 6,
         height = 6,
         units = "in"
  )

@@

# Per Stock
stock_d <-  Eme_Res %>% 
  left_join(Neighbours) %>% 
    # distinct(taxon_key,neighbour_id, .keep_all = TRUE) %>% 
    group_by(taxon_key,tresh) %>% 
    summarise(
      taxon_emer = min(emerging_yr)
    ) %>% 
    group_by(taxon_emer,tresh) %>% 
  summarise(
    n_tax = n()
  ) %>% 
  group_by(tresh) %>% 
  mutate(
    com_sum = cumsum(n_tax),
    level = "Stock"
  )

  #  EEZ data
eez_d <-  Eme_Res %>% 
  left_join(Neighbours) %>% 
  filter(n_ens == 10) %>% 
    # distinct(eez_name,neighbour_id, .keep_all = TRUE) %>% 
    group_by(sf_eez_name,tresh) %>% 
    summarise(
      taxon_emer = min(emerging_yr)
    ) %>% 
    group_by(taxon_emer,tresh) %>% 
  summarise(
    n_tax = n()
  ) %>% 
  group_by(tresh) %>% 
  mutate(
    com_sum = cumsum(n_tax),
    level = "EEZ"
  )

# Plot Data
plot_data <- stock_d %>% 
  bind_rows(eez_d) %>% 
  filter(tresh != "NA") %>% 
  mutate(
    total = ifelse(level == "Stock",length(unique(Eme_Res$taxon_key)),length(unique(Eme_Res$eez_name))),
    per = com_sum/total*100
  ) ;plot_data

  # filter(emerging_yr >= 2020) %>% 
  ggplot() +
    geom_area(data = subset(plot_data, level == "Stock"),
              aes(
                x = as.numeric(taxon_emer),
                y = com_sum,
                fill = level
              ),
              alpha= 0.8,
              size=0.5,
              colour="black"
    )  +
    geom_area(data = subset(plot_data, level == "EEZ"),
              aes(
                x = taxon_emer,
                y = com_sum,
                fill = level
              ),
              alpha= 0.8,
              size=0.5,
              colour="black"
    ) +
    facet_wrap(~tresh) + 
    # Comment out for option A (Change plot name!!)
  #   geom_hline(yintercept = length(unique(Eme_Res$eez_name)), color = "grey",linetype = "dashed") +
  # geom_text(aes(label="Total number of EEZs", x = 2010, y = length(unique(Eme_Res$eez_name))+10), color = "grey70",size =3) +
  #   geom_hline(yintercept = length(unique(Eme_Res$taxon_key)), color = "grey",linetype = "dashed") +
  # geom_text(aes(label="Total number of Taxa", x = 2010, y = length(unique(Eme_Res$taxon_key))+10), color = "grey70",size =3) +
    scale_y_continuous("Cumulatuve Curve",
                       breaks = seq(0,600,50),
                       limits = c(0,600)
    ) +
    scale_x_continuous("Year of emergence",
                       breaks = seq(2005,2100,10),
                       limits = c(2005,2100)
    ) +
    my_ggtheme_p() +
    scale_fill_viridis(discrete = T) +
  ggsave("./Figures/figure_accumulative_curve_ab.png",
         width = 6,
         height = 6,
         units = "in"
  )

@@

  # filter(emerging_yr >= 2020) %>% 
  ggplot() +
    geom_area(data = subset(plot_data, level == "Stock"),
              aes(
                x = as.numeric(taxon_emer),
                y = per,
                fill = level
              ),
              alpha= 0.8,
              size=0.5,
              colour="black"
    )  +
    geom_area(data = subset(plot_data, level == "EEZ"),
              aes(
                x = taxon_emer,
                y = per,
                fill = level
              ),
              alpha= 0.8,
              size=0.5,
              colour="black"
    ) +
    scale_y_continuous("Cumulatuve Curve",
                       breaks = seq(0,100,25),
                       limits = c(0,100)
    ) +
    scale_x_continuous("Year of emergence",
                       breaks = seq(2005,2100,15),
                       limits = c(2005,2100)
    ) +
    my_ggtheme_p() +
    scale_fill_viridis(discrete = T) +
    facet_wrap(~tresh) + 
  ggsave("./Figures/Fig4.png",
         width = 8,
         height = 8,
         units = "in"
  )

@@

##### Fig. 3 Mapping the time of emergence

@@

# Per EEZs
Eez_d_hist <- Eme_Res %>% 
  group_by(eezid= eez_id ,sau_fishing_entity,tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(
    mean_yr = mean(emerging_yr,na.rm=T),
    sd_yr = sd(emerging_yr,na.rm=T),
    n_taxa = length(unique(taxon_key))
    ) %>% 
  gather("metric","value",mean_yr:n_taxa) %>% 
  filter(metric != "n_taxa")

# Estimate the value (catch and USD) of emerging species
Eme_value_data <- Eme_Res %>% 
  group_by(sau_fishing_entity,fishing_entity_id,tresh,taxon_key) %>% 
  summarise(n()) %>% 
  left_join(Sau_data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  filter(!is.na(variable)) %>% 
  group_by(sau_fishing_entity,fishing_entity_id,tresh,variable) %>% 
  summarise(
   sum_value = sum(value,na.rm=T),
    n_taxa = length(unique(taxon_key)) 
  )

# Total value of each fishing nation

Total_value <- Sau_data %>% 
  group_by(fishing_entity_id,variable) %>% 
  summarise(tot_value= sum(value,na.rm=T))

Value_map_data <- Eme_value_data %>% 
  left_join(Total_value,
            by = c("fishing_entity_id","variable")) %>% 
  mutate(participation = (sum_value/tot_value)*100)

@@

fish_d_hist <- Eme_Res %>% 
  group_by(sau_fishing_entity,tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(
    value = length(unique(taxon_key))
    ) %>% 
  filter(!is.na(sau_fishing_entity))

@@

ggplot(subset(eez_d_hist, tresh == "Tresh_one")) +
  geom_density(
    aes(
      x = value,
      fill = tresh
    ),
    bins = 10,
    alpha = 0.8
  ) +
  facet_wrap(~metric,
             scales = "free") +
  scale_fill_viridis(discrete = T) +
  my_ggtheme_p() +
  ggsave("./Figures/hist_mean.png",
         width = 6,
         height = 6,
         units = "in"
  )

World_map_nemer <- World_map %>%
  left_join(Value_map_data,
            by = c("sau_fishing_entity","fishing_entity_id")
  )

grey_land <- World_map %>% 
  filter(!fishing_entity_id %in% World_map_nemer$fishing_entity_id)

grey_eez <- World_eez_sf %>% 
  filter(!eezid %in% eez_d_hist$eezid)

@@

  tresh_list <- c("Tresh_one","Tresh_two")
  name_save <- paste("./Figures/emer_map_par_",tresh_list[i],".png",sep = "")

  World_map_nemer <- World_map_nemer %>% 
    filter(
      tresh ==  tresh_list[i], 
      variable == "value"
    )

  map <- World_eez_sf %>% 
    left_join(eez_d_hist,
              by = "eezid") %>% 
    filter(tresh == tresh_list[i],
           metric == "mean_yr") %>% 
    ggplot() +
    geom_sf(
      aes(
        fill = value
      ),
      color =  "white",
      size = 0.1
    ) +
    geom_sf(data = World_map_nemer,
            aes(fill = participation+2000),
            color =  "white",
            size = 0.1
            ) +
    # grey maps
    geom_sf(data = grey_land, aes(),fill = "grey50", color =  "white",size = 0.1) +
    geom_sf(data = grey_eez, aes(),fill = "grey50", color =  "white",size = 0.1) +
    annotate("text", 
             x =(c(-85.5,-30,25,81,136)+5),
             y = -93.5,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100), 
             color="black", 
             size=3, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    scale_fill_viridis(
      limits = c(2000,2100),
      breaks = seq(2000,2100,25)
    ) +
    my_ggtheme_m() +
    ggsave(name_save,
           width = 12,
           height = 10,
           units = "in"
    )
